### 2023-07-13 paper/sec-dis-pseudodata.tex
sect 2 updated

 As we discuss below, the calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors requires two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 In this section, we summarise the main features of each of the ongoing and future
 far-forward detectors considered in this study, in particular concerning
 their acceptance, geometry, and neutrino detection method.
 %
 We also indicate the expected performance of the three FPF detectors
 and how this translates into the dominant experimental systematic
 uncertainties.
 %
 Since for the projection studies considered in this work we focus on muon
 neutrino scattering, we will focus the subsequent discussion on the detection
 performance of this neutrino flavour.

 Table~\ref{tab:FPF_experiments} indicates
 the rapidity coverage, target material,
 muon neutrino acceptance, and the identification and reconstruction performance
 for each of the far-forward LHC neutrino experiments considered
 in this work.
 %
 More details of the information listed in this table is provided
 in the following.

  %-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.50}
\begin{tabularx}{\textwidth}{Xccccc}
\toprule
Detector &  Rapidity &  Target & Charged Lepton ID & Acceptance  & Performance \\
\midrule
\midrule
\multirow{2}{*}{FASER$\nu$}  &  \multirow{2}{*}{ $|\eta_\nu| \le 8.5$}  &   Tungsten  & \multirow{2}{*}{muons}      &   $E_\ell \gsim 100$ GeV   &    \multirow{2}{*}{n/a}       \\
  &   &   (1.1 ton)  &       &  $\tan \theta_\ell \lsim 0.5$   &         \\
\midrule
\multirow{2}{*}{SND@LHC}  & \multirow{2}{*}{ $7.2 \le \eta_\nu \le 8.4$}   &  Tungsten   &   \multirow{2}{*}{n/a}    &  $E_\mu \gsim 20 $ GeV     &    \multirow{2}{*}{n/a}    \\
  &    &  (0.83 ton)   &  &  $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$         &       \\
\midrule
\midrule
\multirow{3}{*}{FASER$\nu$2}  & \multirow{3}{*}{ $|\eta_\nu| \le 8.5$}  & \multirow{2}{*}{Tungsten}    &   \multirow{3}{*}{muons}     &   $E_\ell \gsim 100$ GeV  &    $\delta E_\ell \sim 30\% $     \\
  &   &  \multirow{2}{*}{(20 ton)}   &       &  $\tan \theta_\ell \lsim 0.5$   &   $\delta \theta_\ell \sim 1$ mrad      \\
  &   &     &       &  reconstructed $E_h$ \& charm ID   &  $\delta E_h \sim 30\%$        \\
\midrule
\multirow{3}{*}{AdvSND~(far)}  &   \multirow{3}{*}{ $7.2 \le \eta_\nu \le 8.4$}  &
\multirow{2}{*}{Tungsten}   &   \multirow{3}{*}{muons}    &  $E_\mu \gsim 20 $ GeV  & \multirow{3}{*}{n/a}          \\
  &   &   \multirow{2}{*}{(5 ton)}  &        & $\theta_\mu \lsim 0.15, \theta_e \lsim 0.5$     &           \\
  &   &     &       &  reconstructed $E_h$   &           \\
\midrule
\multirow{3}{*}{FLArE}  & \multirow{3}{*}{tbd} & \multirow{2}{*}{Liquid Argon}  & \multirow{3}{*}{ maybe muons}  &  $E_\mu \lsim 2$ GeV, $E_e \lsim 1$ TeV    &    $\delta E_e \sim 5\% $ \\
&   &  \multirow{2}{*}{(10 ton)}   &   & $\theta_\mu \lsim 0.4$, $\theta_e \lsim 0.5$ &    $\delta \theta_e \sim 15 $ mrad   \\
 &   &     &  & reconstructed $E_h$  &    $\delta E_h \sim 30\% $   \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small For each of the far-forward LHC neutrino experiments considered
  in this work, we indicate their neutrino pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos, while tau neutrinos have lower production rates and are not considered in this study.
  %
  See the description of each experiment in the text for more details.
  %
  For the projections in this work we assume that FASER$\nu$ and SND@LHC acquire data
  for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
  for the complete HL-LHC period.
  %
  An estimate of the expected 
  systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
  which nevertheless are limited by statistics.
  \label{tab:FPF_experiments}
}
\end{table}
%-----------------------------------------------------------------

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis LOS  and have been taking data since the begin of Run III.
%
Neutrino scattering takes place in the FASER$\nu$
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
%
The FASER/FASER$\nu$ apparatus is immersed in a magnetic field which enables charged lepton
identification, provided by two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.

@@

\paragraph{FASER$\nu$2.}
%
A 20-ton neutrino experiment located on the line of sight (LOS)
of the LHC neutrino beam.
%
It is based on an emulsion-based detector optimised to identify heavy flavor particles, including
tau leptons and charm and beauty particles, arising from neutrino interactions.
%
The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
%
The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.

@@

 \paragraph{FLArE.}
 %
 Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment relies on a modularized liquid argon (LAr) time projection detector.
 %
 The use of LAr as target is particularly beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
 %
 FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
 while  fully containing the events as required for kinematic reconstruction.
 %
 The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
 for muon charge and momentum measurements.
 %
 With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
 detect muon neutrinos with energies  $E_\mu\lsim 1.5~\rm{TeV}$ and
 scattering angles up to 0.4 mrad.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim$30\% of muon energy resolution and
 $\delta \theta_\mu \sim 5$ mrad of muon angular  resolution.

@@

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected precision of DIS structure function
measurements as follows.
%
The goal is to quantify the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\rm ev}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bins} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon and tau neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
The choice of the binning is in principle arbitrary, and here we define them
to ensure that Gaussian statistics hold for all the bins of the measurement.

In this calculation we assume the neutrino fluxes provided by the calculation
of~\cite{Kling:2021gos} and neglect the associated uncertainties.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
As we further discuss in Sect.~\ref{sec:settings}, theoretical predictions
for the latter are computed with {\sc\small YADISM} interfaced to {\sc\small PineAPPL}
to produce fast precomputed interpolation grids.
%
Differential event yields are therefore evaluated using
\begin{equation}
  \label{eq:event_yields}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
\end{equation}
with $n_T$ is the nuclear density of the target detector material and $L_T$ its length.
%
The incoming neutrino fluxes, which include the geometric acceptance of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We consider the scattering of muon neutrinos, characterised by the highest rates, and in some cases
we present results also for electron neutrinos.
%
We have verified that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields}), when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv}.
%
The triple integral in  Eq.~(\ref{eq:event_yields}) is evaluated numerically by means
of Monte Carlo sampling, by generating sampling $N_{\rm mc}$ points in the $\lp x,Q^2,E_{\nu}\rp$ space
with the constraint that $0 < y = Q^2/2m_N E_{\nu }x <1 $
and then  integrating over the bin range:
\begin{equation}
    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) \, ,
    \label{MCintegration}
\end{equation}
and where $N_{\rm mc}$ is chosen to be large enough such that residual Monte Carlo integration
uncertainties are negligible.

Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors considered
  in the present analysis, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  restriction that the momentum transfer and the final-state invariant mass should be restricted
  to the DIS region,
  \be
  \label{eq:DISconditions}
Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 12.5~{\rm GeV}^2 \, .
\ee
  %
  As discussed above, for FASER$\nu$ and SND@LHC we assume the integrated luminosity to
  be that of Run III while for the FPF experiments we assume the full HL-LHC
  luminosity (3 ab$^{-1}$).
  %
   The numbers in parenthesis indicate the event rates corresponding to charm
  production for those experiments with heavy flavour tagging capabilities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------------
\begin{table}[t]
  \centering
  \small
  \renewcommand{\arraystretch}{1.60}
\begin{tabularx}{\textwidth}{X|c|c|c|c|c|c}
\toprule
Detector & $\quad$ $N_{\nu_e}$ $\quad$ &$\quad$ $N_{\bar{\nu}_e}$$\quad$   &   $N_{\nu_e} + N_{\bar{\nu}_e}$ &
$\quad$$N_{\nu_\mu}$ $\quad$ & $\quad$ $N_{\bar{\nu}_\mu}$ $\quad$  &   $N_{\nu_\mu} + N_{\bar{\nu}_\mu}$ \\
\midrule
FASER$\nu$  &    &    &   &   &    &    \\
SND@LHC  &    &    &   &   &    &    \\
\midrule
FASER$\nu$2  &    &    &   &   &    &    \\
AdvSND~(far)  &    &    &   &   &    &    \\
FLArE &    &    &   &   &    &    \\
  \bottomrule
\end{tabularx}
\vspace{0.2cm}
\caption{\small The predicted integrated event yields for the five detectors considered
  in the present analysis, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  restriction that the momentum transfer and the final-state invariant mass be restricted
  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
  %
  The numbers in parenthesis indicate the event rates corresponding to charm
  production.
  \label{tab:integrated_rates}
}
\end{table}
%-----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Eq.~(\ref{eq:event_yields}) can be generalised to charm-production events, with
the only difference being that now the neutrino scattering cross-section is restricted
to those processes leading to final-state charm quarks.
%
Assuming that charm quarks can be directly tagged by the detector one has
\be
\label{eq:event_yields_charm}
  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, 
  \ee
  with the charm production cross-sections being discussed in~\cite{Faura:2020oom}
  and references therein.
  %
  Detectors without charm-tagging capabilities can still be sensitive to charm production via
  the semileptonic decays of the $D$-mesons, resulting in the characteristic
  dimuon topology, where
  \be
 N_{\rm ev,2\mu}^{(i)} \approx N_{\rm ev,c}^{(i)} \times \mathcal{B}\lp c \to D \to \mu + X\rp \, ,
 \ee
 with $\mathcal{B}$ a numerical factor that accounts for charm hadronisation and the
 resulting semileptonic decay to a muon.
 %
 Given that $\mathcal{B}\sim 0.1$, being able to tag directly charm quarks increases the event yields
 of charm production events by a factor of 10 as compared to reconstructing the dimuon final state.
 %
 Here we neglect finite acceptance effects, which can only be properly estimated by means
 of a full detector simulation.

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos detected at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrated over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos as indicated in Table~\ref{tab:integrated_rates}.
  %
  Kinematic cuts are such that the DIS conditions in Eq.~(\ref{eq:DISconditions}) are satisfied.
  %
  Only bins with at least 30 events are retained.
  %
  One can observe the large event rates for most of the region in $\lp x,Q^2\rp$ covered,
  which result into very competitive statistical uncertainties.
  %
  From Fig.~\ref{fig:fasernu2_muon} we see that the kinematic coverage of FASER$\nu$2 is
  $x_{\rm min}\sim 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ at large-$Q^2$, which represent an extension
  of around one order of magnitude in both directions as compared to available
  DIS neutrino data.

%-----------------------------------------------------------------------
\begin{figure}[!ht]
    \centering
\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{\small The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos. }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

>>>>

 The calculation of differential neutrino scattering event rates
 at the LHC far-forward detectors involves two main ingredients: the energy
 and flavour dependence of the incoming neutrino flux crossing
 the detector fiducial volume, on the one hand,
 and the scattering rates within the same fiducial volume, on the other hand.
 %
 In this section, we summarise the main features of each of the existing and future
 far-forward detectors considered in this study, in particular concerning
 their acceptance, performance, and detection method.
 %
 We focus on  muon
 neutrino scattering, which benefits from the highest rates and is less
 affected by uncertainties affecting $D$-meson production.

 The kinematics of a charged-current neutrino DIS event $(x,Q^2, E_\nu)$,
 or alternatively $(x,Q^2, y)$, are uniquely specified by the measurement of three independent
 final-state variables,
 such as $\lp E_\ell,\theta_\ell, W^2\rp$ or $\lp E_\ell,\theta_\ell, E_h \rp$,
 with $E_\ell$ and $\theta_\ell$ being the energy and polar angle of the outgoing
 charged lepton and $E_h$ the total energy of the hadronic final state.
 %
 Most neutrino detectors can only access $E_h$, given that $W^2$ requires
 fully reconstructing this final state.
 %
 A measurement of  $\lp E_\ell,\theta_\ell, E_h \rp$ then fixed the DIS kinematics as:
 \bea
 E_\nu &=& E_h + E_\ell \, , \nonumber \\
 Q^2 &=& 4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp \, ,\\
 x&=& \frac{4 ( E_h + E_\ell) E_\ell \sin^2 \lp \theta_\ell/2\rp}{2m_N E_h} \, .\nonumber
 \eea
 These relations also indicate how systematic uncertainties affecting the measurement
 of $\lp E_\ell,\theta_\ell, E_h \rp$ translate into uncertainties in the
 reconstructed values of  $(x,Q^2, E_\nu)$, which in turn modify the expected
 event rates in a given bin.

 Table~\ref{tab:FPF_experiments} indicates,
for each of the far-forward LHC neutrino experiments considered
  in this work,  their neutrino pseudo-rapidity coverage, target material, whether
  they can identify the sign of the outgoing charged lepton,
  the acceptance for the charged lepton and hadronic final state,
  and the expected reconstruction performance.
  %
  We consider separately acceptance and performance for electron and muon
  neutrinos, while tau neutrinos have lower production rates and are neglected in this study.
  %
  For these projections we assume that FASER$\nu$ and SND@LHC acquire data
  for the full Run III period, while FASER$\nu$2, AdvSND, and FLArE take data
  for the complete HL-LHC period.
  %
  An estimate of the expected 
  systematic uncertainties is not available for FASER$\nu$ and SND@LHC, experiments
  which are nevertheless limited by statistics.
  %
  In the following we provide more details about the information collected in
  Table~\ref{tab:FPF_experiments}.

%---------------------------------------------------
  \input{tables/detectors.tex}
%---------------------------------------------------

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the begin of Run III.
%
Neutrino scattering takes place in the FASER$\nu$
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.

@@

\paragraph{FASER$\nu$2.}
%
A proposed 20-ton neutrino experiment located on the LOS
of the LHC neutrino beam to be installed in the FPF cavern.
%
It is based on an emulsion-based detector optimised to identify heavy flavor particles, including
tau leptons and charm and beauty particles, arising from neutrino interactions.
%
The FASER$\nu$2 detector is composed of 3300 emulsion layers interleaved with 2-mm-thick tungsten plates,
for a total volume of  tungsten of $40~\rm{cm} \times 40~\rm{cm} \times 6.6~{\rm m}$.
%
The combination of FASER$\nu$2  with the nearby FASER2 detector, equipped with a spectrometer, makes measurements of the outgoing muon charge possible.

@@

 \paragraph{FLArE.}
 %
 Building upon recent progress in liquid noble gas neutrino detectors over the last decade (ICARUS, MicroBooNE, SBND, ProtoDUNE, DUNE), this experiment relies on a modularized liquid argon (LAr) time projection detector.
 %
 The use of LAr as target is beneficial for final-state particle identification, track angle, and kinetic energy measurements with sub-millimeter spatial resolution in all three dimensions.
 %
 FLArE is suitable to identify high-energy neutrinos ($E_\nu \gsim 100$ GeV)  from all three generations
 while  fully containing the events as required for kinematic reconstruction.
 %
 The detector will be equipped with a magnetized hadron/muon calorimeter downstream of the liquid argon volume
 for muon charge and momentum measurements.
 %
 With an expected fiducial (active) mass of 10 tons (30 tons), FLArE will
 detect final-state electrons with energies $E_{e}\lsim 1~\rm{TeV}$ and
 scattering angles up to 0.5 mrad, while detecting final-state muons
 is restricted to $E_{e}\lsim 2~\rm{GeV}$  and $\theta_\mu \lsim 0.4$.
 %
 Reconstruction of the total energy of the hadronic final state will also
 possible. 
 %
 In terms of performance, the targets
 are $\delta E_\mu \sim$5\% of electron energy resolution,
 $\delta \theta_e \sim 15$ mrad of electron angular  resolution,
 and $\delta E_h \sim 30$\% for the hadronic energy.

@@

For each of the LHC far-forward neutrino detectors
described in Table~\ref{tab:FPF_experiments}, we generate
projections for the expected precision of DIS structure function
measurements as follows.
%
The goal is to evaluate the number of reconstructed charged-current neutrino interaction
events taking place in the fiducial volume of the detector in bins of Bjorken-$x$,
momentum transfer $Q^2$, and neutrino energy $E_\nu$, that is,
\be
\label{eq:event_yields}
N_{\rm ev}^{(i)}\lp \nu_e ; E_{{\rm min}}^{(i)} \le E_\nu \le E_{{\rm max}}^{(i)} ,\,
x_{{\rm min}}^{(i)} \le x \le x_{{\rm max}}^{(i)} ;\, Q_{{\rm min}}^{2(i)} \le Q^2 \le Q_{{\rm max}}^{2(i)}\rp
\, ,\quad i=1,\ldots, N_{\rm bins} \, ,
\ee
for electron neutrinos and for each of the bins composing the measurement, and with similar
expressions applying for muon and tau neutrinos and antineutrinos.
%
These event yields determine the statistical
precision associated to a measurement of the double-differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
Subsequently, we account for the expected reconstruction performance of the detector
in order to estimate the systematic uncertainties associated to these event yields.
%
The choice of the binning is in principle arbitrary, and here we define them
to ensure that Gaussian statistics hold for all the bins of the measurement.

In this calculation, we assume the central values of the neutrino fluxes provided by the calculation
of~\cite{Kling:2021gos}.
%
The bin-by-bin integrated event yields in Eq.~(\ref{eq:event_yields}) are
obtained by convoluting the incoming neutrino fluxes, for a given geometric acceptance
of the target detector, with the corresponding neutrino differential cross-sections
Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}).
%
As we further discuss in Sect.~\ref{sec:settings}, theoretical predictions
for the latter are computed with {\sc\small YADISM} interfaced to {\sc\small PineAPPL}
to produce fast precomputed interpolation grids.
%
Differential event yields are therefore evaluated using
\begin{equation}
  \label{eq:event_yields}
   N_{\rm ev}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, ,\quad i=1,\ldots, N_{\rm bins} \, ,
\end{equation}
with $n_T$ is the nuclear density of the target detector material and $L_T$ its length.
%
The incoming neutrino fluxes, which include the geometric acceptance of the considered detector,
are encoded in $dN_{\nu}(E_\nu)/dE_{\nu}$.
%
We consider only the scattering of muon neutrinos, characterised by the highest rates.
%
We verify that the differential event yield calculation
implemented in Eq.~(\ref{eq:event_yields}), when extrapolated to a single bin
covering the full detector acceptance,
is consistent with the fiducial interaction rates presented in~\cite{Feng:2022inv}.

The triple integral in  Eq.~(\ref{eq:event_yields}) is evaluated numerically by means
of Monte Carlo sampling, by generating sampling $N_{\rm mc}$ points in the $\lp x,Q^2,E_{\nu}\rp$ space
with the constraint that $0 < y = Q^2/2m_N E_{\nu }x <1 $
and then  integrating over the bin range:
\begin{equation}
    N_{\rm ev}^{(i)} \approx n_T L_T \frac{(Q^{2(i)}_{\rm max}-Q^{2(i)}_{\rm min})(x^{(i)}_{\rm max}-x^{(i)}_{\rm min})(E_{\rm max}^{(i)}-E_{\rm min}^{(i)})}{N_{\rm mc}}\times \sum_{j=1}^{N_{\rm mc}} \frac{dN_{\nu}(E^{(j)}_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma(x^{(j)},Q^{2(j)},E^{(j)}_{\nu})}{dxdQ^2}\right) \, ,
    \label{MCintegration}
\end{equation}
and where $N_{\rm mc}$ is chosen to be large enough such that residual Monte Carlo integration
uncertainties are negligible for all the bins considered.

Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors
considered, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  requirement that the momentum transfer and the final-state invariant mass are restricted
  to the DIS region,
  \be
  \label{eq:DISconditions}
Q^2 \ge 2~{\rm GeV}^2\quad{\rm and}\quad  W^2 \ge 4~{\rm GeV}^2 \, .
\ee
  %
   The numbers in parenthesis indicate the event rates corresponding to charm
  production, for those experiments with heavy flavour tagging capabilities.

%----------------------------------------------------
\input{tables/integrated_yields.tex}
%----------------------------------------------------

Eq.~(\ref{eq:event_yields}) can be generalised to charm-production events, with
the only difference being that now the neutrino scattering cross-section is restricted
to those processes leading to final-state charm quarks.
%
Assuming that charm quarks can be directly tagged by the detector one has
\be
\label{eq:event_yields_charm}
  N_{\rm ev,c}^{(i)} = n_T L_T\int_{Q^{2(i)}_{\rm min}}^{Q^{2(i)}_{\rm max}}\int_{x^{(i)}_{\rm min}}^{x^{(i)}_{\rm max}}\int_{E_{\rm min}^{(i)}}^{E_{\rm max}^{(i)}} \frac{dN_{\nu}(E_\nu)}{dE_{\nu}}\left(\frac{d^2\sigma^{\nu N \to \ell + c+X}(x,Q^2,E_{\nu})}{dxdQ^2}\right) dQ^2 dx dE_{\nu} \, 
  \ee
  with the charm production cross-sections discussed in~\cite{Faura:2020oom}
  and references therein.
  %
  Detectors without charm-tagging capabilities can still be sensitive to charm production via
  the semileptonic decays of the $D$-mesons, resulting in the characteristic
  dimuon topology, where
  \be
 N_{\rm ev,2\mu}^{(i)} \approx N_{\rm ev,c}^{(i)} \times \mathcal{B}\lp c \to D \to \mu + X\rp \, ,
 \ee
 with $\mathcal{B}$ a numerical factor that accounts for charm hadronisation and the
 resulting semileptonic decay to a muon.
 %
 Given that $\mathcal{B}\sim 0.1$, being able to tag directly charm quarks increases the event yields
 of charm production events by a factor of 10 as compared to reconstructing the dimuon final state.
 %
 Here we neglect finite acceptance effects, which can only be properly estimated by means
 of a full detector simulation.

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos detected at FASER$\nu$2 restricted
  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
  %
  We present results binned in $x$ and $Q^2$ and integrated over all available neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into the $N_{\nu_\mu}$ value
  for reconstructed muon
  neutrinos listed in
  Table~\ref{tab:integrated_rates}.
  %
  Only bins with at least 30 events are retained, to ensure the validity of Gaussian
  statistics.
  %
  One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
  leading to typical statistical uncertainties at the 1\% level or smaller.

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
\includegraphics[width=0.8\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{\small The event yields per bin $N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at the FASER$\nu$2 detector, restricted
  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
  %
  We present results binned in $x$ and $Q^2$ integrated over neutrino energies.
  %
  The red dots indicate the weighted bin center.
  %
  Adding up all the bins in this plot results into the $N_{\nu_\mu}$ value listed in
Table~\ref{tab:integrated_rates}.}
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

Fig.~\ref{fig:fasernu2_muon} indicates
how the kinematic coverage of FASER$\nu$2 reaches
$x_{\rm min}\sim 3\times 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 2\times 10^3$
at large-$Q^2$, representing an extension
of around one order of magnitude in both directions as compared to available
DIS neutrino data on nuclear targets.
%
Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF} compares
the kinematic coverage of FASER$\nu$2 with that of electron-ion collisions
at the upcoming EIC~\cite{Khalek:2021ulf,AbdulKhalek:2021gbh}
and to other available hard-scattering datasets involving
nuclear targets or projectiles.
%
Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
production in proton-lead collisions at the LHC entering the  nNNPDF3.0
determination~\cite{AbdulKhalek:2022fyi}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.8\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,
      same as  Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Statistical and systematic uncertainties}
\label{subsec:uncertainties}
